Strings functions analysis

### 2022-08-22 article.tex
table moved to Appendices section
Acknowledgements added

    To avoid self-repeats, a summary list of the functions to be analyzed is presented in Section 8.

@@

@@

    \begin{enumerate}
        \item Set is initially empty.
        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 3.5.2, it is added to the set.
        \item The second step is repeated until there are no unselected functions left.
        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 3.5.2 are removed.
    \end{enumerate}

@@

    Below is a table with the results - metrics.

@@

    \section{Used materials}

>>>>

    To avoid self-repeats, a summary list of the functions to be analyzed is presented in section \ref{table 1}.

@@

    \label{criterion}

@@

    \begin{enumerate}
        \item Set is initially empty.
        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion \ref{criterion}, it is added to the set.
        \item The second step is repeated until there are no unselected functions left.
        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion \ref{criterion} are removed.
    \end{enumerate}

@@

    Below in section \ref{table 1} is a table with the results - metrics.

    \section{Acknowledgements}

    The research was funded by Huawei Technologies Co. Ltd.

    \section{References}

    \section{Appendices}

    \label{table 1}

@@
